Redundant calibration as a complex optimization problem

### 2016-12-06 paper.tex
started adding some historical overview to red calibration paper

[Redundant calibration has been in use for a long time. In the early 1980's it was already used to produce high-dynamic range images of 3C84.] RW The first 
implementations of redundant calibration made use of the logarithm function, because when the logarithm is applied to the scalar measurement equation redundant 
calibration is transformed into a linear problem cite Wieringa,camps and Lui. This approach is also generally referred to as LOGCAL.
LOGCAL is reviewed in Appendix ??. The next improvement was to perform a firt-order taylornomial expansion (which is equivalent to the GN algorithm Kurien 2016) of the measurement equation an then to solve for the
perturbations of the model-parameters. This approach is commonly referred to as LINCAL. LINCAL is derived from first principals in Appendix . Two ways of speeding up redundant calibration has also been 
proposed. The first technique makes use of the alternating direction implicit method, in which we alternate between solving the gains, their conjugates and 
the true observed visibilities (wijnholds and marthi). Using the conjugate gradient method to exploit the sparsity inherent in the redundant calibration problem, 
and in doing so speedup the algorithm itself was proposed in . A proper comparison of between these two approaches have not been done before.

>>>>

[Redundant calibration has been in use for a long time. It was already being used in the 1980's. Noordam used redundant calibration to produce high-dynamic range images of 3C84 with the 
WSRT array.] RW The first implementations of redundant calibration made use of the logarithm function, because when the logarithm is applied to the scalar measurement equation redundant 
calibration is transformed into a linear problem cite Wieringa,camps and Lui. This approach is also generally referred to as LOGCAL.
LOGCAL is reviewed in Appendix ??. The next improvement was to perform a firt-order taylor expansion (which is equivalent to the GN algorithm Kurien 2016) of the measurement equation an then to solve for the
perturbations of the model-parameters. This approach is commonly referred to as LINCAL. LINCAL is derived from first principals in Appendix . Two ways of speeding up redundant calibration has also been 
proposed. The first technique makes use of the alternating direction implicit method, in which we alternate between solving the gains, their conjugates and 
the true observed visibilities (wijnholds and marthi). Using the conjugate gradient method to exploit the sparsity inherent in the redundant calibration problem, 
and in doing so speedup the algorithm itself was proposed in . A proper comparison between these two approaches has not been done before.

Newly built instruments like LOFAR, ..... has also sparked a renewed interest in redundant calibration. Redundancy is also advantageous for detecting the EoR,
which explains why some of the previsously mentioned instruments have redundant layouts.
